### 2014-11-17 Neutral_simulPow.Rmd
Add figures of neutral spatpatt Dq & RAD

>>>>

## Simulations to plot spatial patterns with differents replacement Rate

```{r neutral_SpSimPlot256, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

# meta = 64, side=250, time=500
sad64 <- simul_NeutralSAD(64,256,500)

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1))
g

setwd("..")
ggsave("spat_NeuLog64_256.png", width=8,height=6,units="in",dpi=600)

setwd("Simul")

plotNeutral_Dq(64,256,500,"L",NULL) # Null use previous simulations

setwd("..")
ggsave("Dq_NeuLog64_256.png", width=8,height=4,units="in",dpi=600)

### Plot Average SAD!
setwd("Simul")
den <- plotNeutral_SAD(0,256)

setwd("..")
ggsave("RAD_NeuLog_spMeta_256.png", width=8,height=6,units="in",dpi=600)

# USAR dplyr en calcRankSAD_by (ver SP_simul 428)
```
